Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-20 paper/main.tex
more slice info

\emph{Slice} (TODO - Leon can you expand this? What did you base our slicing on?)
The goal of this feature is to help eliminate terms that cannot be the source of
the crash. These include lines that are never run, lines that run successfully
and don't affect any variables that are used later, and so on. More specifically, we
build up a dependency graph of all lines in the program trace. Edges in the graph
represent either def-use dependence or control-flow dependence. Then ideally,
any node in the graph that is not a transitive dependency of the line that crashes
can't be responsible for the crash. However dynamic slicing is not perfect (TODO
include example?), so unlike in prior work, we do not treat membership in the slice
as a hard constraint.

@@

\bibliographystyle{abbrv}
\bibliography{nanomaly,sw,temp}

>>>>

\emph{Slice}
\begin{figure}
\begin{lstlisting}
x = input() # The user inputs 0
if x != 0:
  x = 1
print("One divided by your number is: %d" % (1 / x))
\end{lstlisting}
\caption{In this program, the programmer may have intended the placeholder
  assignment \texttt{x = 1} to be used in case the user input 0, and used the
  incorrect condition \texttt{x != 0}, rather than \texttt{x == 0}. However, the
  condition expression will not be included in the slice (which would include
  lines 1 and 4), because the presence of
  the conditional does not affect the behavior of the program.
}
\label{slice-downside-example}
\end{figure}

\begin{figure}
\begin{lstlisting}
while true:
  x = input()
  if x != 0:
    break
  print("One divided by your number is: %d" % (1 / x))
\end{lstlisting}
\caption{
  This program's mistake is the same as before,
  but instead they try to handle the
  bad input by breaking out of the input loop. When computing the slice, our
  method would record a control dependency between the condition on line 3 and
  the print statement on line 5, placing the bad condition in the program slice.
}
\label{early-break}
\end{figure}

The goal of this feature, roughly equivalent in purpose to the type error slice in
\cite {learning-to-blame}, is to help eliminate terms that cannot be the source of
the crash. We compute a dynamic program slice \cite{KOREL1988155}, the set of
terms that contributed at runtime to the observed exception, and turn this
feature on for terms in the slice. We follow the basic approach of
\cite{KOREL1988155, KOREL1990187}, building a graph of data and control
dependencies. We then traverse the graph backwards, starting at the execution
step where the error occurred, to collect the set of terms that the excepting
line transitively depended on. This excludes lines that could not have caused the
exception, such as lines that never ran, or lines that ran but had no connection
to the step where the exception happened.

A downside of using the dynamic slice, in the case of control dependencies, is
that it excludes terms whose presence does not affect whether the exception
happened, but which could have had an effect if the term was different. In
\figref{slice-downside-example}, the conditional statement is never run, so the
removal of the conditional would not have any effect on the program's behavior,
and it would not be included in the program slice. The dynamic slice misses the
incorrect test condition because the mistake itself caused the conditional
statement and its body to become irrelevant.

To overcome this issues in the ``early return'' or ``early break'' case
(\figref{early-break}), we check if a break, return, or other statement for
breaking out of structured control flow is present inside of a conditional
statement. We then add dependencies in the execution trace's dependency graph
between the enclosing conditional and the statements that would have been skipped
by the break or return. This is insufficient to overcome all related problems,
however, so unlike in prior work, we do not treat membership in the slice
as a hard constraint.

@@

\bibliographystyle{abbrv}
\bibliography{nanomaly,sw,temp,slice}
